On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-01 main.tex
Minor edits

% new commands and shortcuts
\def\bs{\textit{\textbf{s}}}
\def\Lb{\textit{\textbf{L}}}
\def\Xb{\textit{\textbf{X}}}
\def\xb{\textit{\textbf{x}}}
\def\fb{\textit{\textbf{f}}}
\def\ab{\textit{\textbf{a}}}
\def\ajb{\overline{a_j}}
\def\bjb{\overline{b_{j,l}}}
\def\pjb{\overline{P_{j}}}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\htt}{ht}
\def\C{\mathbb{C}}
\def\vt{\vartheta}
\def\Q{\mathbb{Q}}
\def\R{\mathbb{R}}
\def\rs{\mathscr{R}}
\def\P{\mathscr{P}}
\def\d{\delta}
\def\sing{ \textrm{sing}}
\def\codim{ \textrm{codim}}
\def\jac{ \textrm{jac}}
\def\exp{\textrm{exp}}
\def\grad{\textrm{grad}}
\def\rank{\textrm{rank}}
\def\reg{\textrm{reg}}
\def\jt{\widetilde{J}}
\def\At{\widetilde{A}}
\def\Yt{\widetilde{Y}}
\def\dt{\widetilde{d}}
\def\Dt{\widetilde{D}}
\def\rk{\textrm{rank }}
\def\pa{\partial}
\def\D{\Delta}
\def\Z{\frak{Z}}
\def\I{\frak{I}}
\def\Is{\frak{I}^{\star}}
\def\A{\frak{A}}
\def\fp{\frak{P}}
\def\sp{\mathscr{P}}
\def\la{\langle}
\def\ra{\rangle}
% matrices 
\def\bbm{\begin{bmatrix}}
\def\ebm{\end{bmatrix}}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Bit Complexity for Computation of one Point in each Connected Component of a Smooth Real Hypersurface}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
We provide bit complexity estimates for the computation of at least one point in each connected component of a smooth real hypersurface. This problem is a basic and important subroutine used in semi-algebraic geometry. For instance, it is used in determining an upper bound on the number of connected components of a real hypersurface. The algorithm requires some genericity properties, which we ensure through random changes of variables that produce generic coordinate systems. In order to ensure these properties with arbitrarily high probability, we developed a new quantitative extension of Thom's weak transversality theorem, and a new quantitative Noether normalization statement for polar varieties. These statements enable us to give a precise probability analysis of a monte carlo algorithm, where we can guarantee correctness with arbitrarily high probability. 
\par
Algorithms for deciding connectivity queries in real algebraic geometry have been developed in a series of papers \cite{a,b,c,d}. However, these algorithms are based in the arithmetic complexity model, and bit complexity questions were left for future work.  Our results therefore begin to fill a missing gap in the research. 
%Furthermore, as bit complexity provides a far more realistic model of computation compared to arithmetic complexity, which only counts each operation at unit cost whereas bit complexity provide more information for both time and space resources that are needed in practice, it is important that this missing gap is filled. 
%As bit complexity provides a far more realistic model of computation compared to arithmetic complexity, which only counts each operation at unit cost, our contribution is necessary and important. Indeed, bit estimates provide more information for both time and space resources that are needed in practice. 
\end{abstract}

@@

\nl Use \cite{AD} to compute the partial derivatives $\frac{\pa f^A}{\pr X_{i+1}},\hdots,\frac{\pa f^A}{\pr X_n}$\;

@@

>>>>

\usepackage{mathrsfs}
% new commands and shortcuts
\def\bs{\textit{\textbf{s}}}
\def\Lb{\textit{\textbf{L}}}
\def\Xb{\textit{\textbf{X}}}
\def\xb{\textit{\textbf{x}}}
\def\fb{\textit{\textbf{f}}}
\def\ab{\textit{\textbf{a}}}
\def\ajb{\overline{a_j}}
\def\bjb{\overline{b_{j,l}}}
\def\pjb{\overline{P_{j}}}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\htt}{ht}
\def\C{\mathbb{C}}
\def\vt{\vartheta}
\def\Q{\mathbb{Q}}
\def\R{\mathbb{R}}
\def\rs{\mathscr{R}}
\def\P{\mathscr{P}}
\def\d{\delta}
\def\sing{ \textrm{sing}}
\def\codim{ \textrm{codim}}
\def\jac{ \textrm{jac}}
\def\exp{\textrm{exp}}
\def\grad{\textrm{grad}}
\def\rank{\textrm{rank}}
\def\reg{\textrm{reg}}
\def\jt{\widetilde{J}}
\def\At{\widetilde{A}}
\def\Yt{\widetilde{Y}}
\def\dt{\widetilde{d}}
\def\Dt{\widetilde{D}}
\def\rk{\textrm{rank }}
\def\pa{\partial}
\def\D{\Delta}
\def\Z{\frak{Z}}
\def\I{\frak{I}}
\def\Is{\frak{I}^{\star}}
\def\A{\frak{A}}
\def\fp{\frak{P}}
\def\sp{\mathscr{P}}
\def\la{\langle}
\def\ra{\rangle}
% matrices 
\def\bbm{\begin{bmatrix}}
\def\ebm{\end{bmatrix}}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
%\title{Bit Complexity for Computation of one Point in each Connected
%Component of a Smooth Real Hypersurface}
\title{On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  We present a full analysis of an efficient algorithm for the
  computation of at least one point in each connected component of a
  smooth real hypersurface, taking into account bit complexity and
  all coefficient growth.  This problem is a basic and important
  subroutine used in semi-algebraic geometry. For instance, it is used
  in determining an upper bound on the number of connected components
  of a real hypersurface. The algorithm requires some genericity
  properties, which we ensure through random changes of variables that
  produce generic coordinate systems. In order to ensure these
  properties with arbitrarily high probability, we developed a new
  quantitative extension of Thom's weak transversality theorem, and a
  new quantitative Noether normalization statement for polar
  varieties. These statements enable us to give a precise probability
  analysis of a monte carlo algorithm, where we can guarantee
  correctness with arbitrarily high probability.

  Algorithms for deciding connectivity queries in real algebraic
  geometry have been developed in a series of papers
  \cite{a,b,c,d}. However, these algorithms are based in the
  arithmetic complexity model, and analyses of the bit complexity
  questions were left for future work.  Our results are an important
  first step in this analysis.

  % Furthermore, as bit complexity provides a far more realistic model
  % of computation compared to arithmetic complexity, which only
  % counts each operation at unit cost whereas bit complexity provide
  % more information for both time and space resources that are needed
  % in practice, it is important that this missing gap is filled.
  % As bit complexity provides a far more realistic model of
  % computation compared to arithmetic complexity, which only counts
  % each operation at unit cost, our contribution is necessary and
  % important. Indeed, bit estimates provide more information for both
  % time and space resources that are needed in practice.
\end{abstract}

@@

\nl Use \cite{AD} to compute the partial derivatives $\frac{\pa f^A}{\Pr X_{i+1}},\hdots,\frac{\pa f^A}{\Pr X_n}$\;

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
